Paper 1

### 2022-06-14 scripts/Paper 1.Rmd
update

cumulative.co2fluxes <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month", "season"), summarise,
        Fco2 = gofC.f(mean(Fco2, na.rm = TRUE)),
        ER = gofC.f(mean(ER_SOLO, na.rm = TRUE)),
        GPP = gofC.f(mean(GPP_SOLO, na.rm = TRUE)))

>>>>

cum.co2fluxes <- input.daily %>%
  ddply(c("Year", "jday", "month"), summarise,
        Fco2 = gofC.f(mean(NEE_LT.gC, na.rm = TRUE)),
        ER = gofC.f(mean(ER_LT.gC, na.rm = TRUE)),
        GPP = gofC.f(mean(GPP_LT.gC, na.rm = TRUE)))
